\cvsection{History}

    \begin{cventries}
    
    \cventry
    {Systems Engineer Lvl. 4}
    {Amazon Inc - Simple Storage Services}
    {Seattle, WA}
    {May 2015 - Sep 2016}
    {
        \begin{cvitems}
        %\item {The S3 Border Reliability team was responsible for ensuring the quality and reliability of border (directly adjacent to an S3 API endpoint that customers use to access S3) networks and services; DNS, specialized top-of-rack routers (QFX5xxx) and x86/DPDK based load balancers, metrics systems to monitor the health and throughput metrics of load balancer sets, as well as older generation load balancer configurations powered by Citrix NetScalers.}
        \item {Planned, scheduled, and configured new hardware in Amazon's data centers around the world to address network capacity needs and initial capacity for introduction of new availability regions.}
        \item {Assisted in the removal and much needed documentation of processes for retiring deprecated infrastructure without affecting customers or other services in the organization.}
        \item {Participated in a 24/7 on-call rotation to address and remediate customer impacting events such as outages, software and hardware faults, and denial of service attacks within service level agreements.}
        \end{cvitems}
    }

    \cventry
    {Software Engineer}
    {ATG Stores Inc - Internal Tools Team}
    {Kirkland, WA}
    {Jan 2014 - May 2014}
    {
        \begin{cvitems}
        \item {Developed applications in .NET for the internal tools team; anything from adding new models and/or business logic in Dynamics AX/GP to a simple FTP client designed specifically for the marketing team.}
        \item {Collaborated with the website team on resolving their backlog items; Javascript errors that occur in specific views and not others, CSS bugs, and minimizing false positives in the logging framework.}
        \item {Left the company to stay for a long term period in Greece with family.}
        \end{cvitems}
    }

    \cventry
    {DevOps / Software Engineer}
    {ConnectXYZ LLC - Direct report to lead systems architect and CEO}
    {Woodinville, WA}
    {Mar 2012 - Jun 2013}
    {
        \begin{cvitems}
        \item {Built server deployment and configuration automation with Opscode Chef on Rackspace infrastructure; this entire stack included HAProxy, nginx, PHP-fpm, Percona XtraDB cluster, Couchbase, OSSEC, munin, and nagios.}
        \item {Developed custom Iptables and ISC Bind 9 chef cookbooks. The iptables cookbook used chef-client registration information together with role-based attributes to determine specific egress and ingress rules on both the internal and external network planes without a need for one-off firewall rules to be specified.}
        \item {Assisted in the development (PHP/Javascript/MySQL) of the platform itself; a cloud-based return merchandise authorization management system.}
        \item {Planned a scheduled launch for a beta release with my team and the service was made available to several clients for trial in December 2012.}
%        \item {Configured and secured/hardened an ElastixPBX instance to terminate a VOIP trunk from MegaPath for the CEO's other company. The configuration included establishing extension plans, IVR, auto attendance, VOIP client software with the G.729 codec, and voicemail.}
        \end{cvitems}
    }

    \cventry
    {Software Engineer}
    {Acronym Media Inc}
    {telecommute}
    {Jan 2011 - Mar 2012}
    {
        \begin{cvitems}
        \item {Assisted in the development of an SEO (KPI and insights dashboarding) analytics platform using PHP Symfony, Highcharts.js, MySQL/Propel.}
        \end{cvitems}
    }

    \cventry
    {Software Engineer part-time}
    {The Branning Group - Consultant to Mr. Branning}
    {telecommute}
    {Jan 2010 - Jan 2011}
    {
        \begin{cvitems}
        \item {Developed on Wordpress, drupal, Joomla, and custom PHP/MySQL/Javascript websites for Mr. Branning and his clients.}
        \end{cvitems}
    }

    \cventry
    {Software Engineer}
    {Onvia Inc - Direct report to lead software architect}
    {Seattle, WA}
    {Nov 2008 - Mar 2009}
    {
        \begin{cvitems}
        \item {Developed a data migration platform in C\#, LINQ, MSSQL, LINQ-to-SQL, WCF, and WPF for the purpose of moving data from an older SQL 2000 database to a newer ORM-based database and production environment.}
        \end{cvitems}
    }

    \cventry
    {IT Manager part-time} 
    {Zion Preparatory Academy - Direct report to the head master} 
    {Seattle, WA} 
    {Dec 2007 - Mar 2010} 
    { 
        \begin{cvitems}
        \item {Managed Active Directory, Exchange Server 2007, Google Apps for Education / non-profits, accounting software, networking, and security for roughly 100 users; the entire K-6 school including faculty and students.}
        \item {Contributed my own hardware with no strings attached for the purpose of getting things done the right way in a low budget environment.}
        \item {Provided help desk and computer repair for all school computers (many rebuilds) running Windows XP with Office, student software, and manged in active directory with several different OUs and varying group policy configurations.}
        \end{cvitems}
    }

    \cventry
    {Software Engineer / Systems Administrator}
    {Seattle Software Systems - Consultant to Mr. Williams} 
    {Seattle, WA} 
    {Oct 2005 - Mar 2007} 
    { 
        \begin{cvitems}
        \item {Developed an inventory management front-end application for PalmOS 4.x in Metrowerks CodeWarrior which ran on Symbol SPT 1846 PalmOS-based PDAs. The application could scan labels for products anywhere with WiFi access around a warehouse and allows for remote management of inventory.}
        \item {Developed in Java, PHP, HTML, CSS, and JavaScript for Mr Williams and his clients.}
        \end{cvitems}
    }

\end{cventries}
